KidsAIR initial SUMs data work

### 2020-01-30 sums_data_cleaning.Rmd
SUMs cleaning and analysis

---
title: "KidsAIR initial SUMs data work"
author: "Ethan Walker"
date: "Started 23 Dec 2019, Updated 14 Jan 2020"
output: pdf_document
---

@@

# Format combined file from above
wmt_sums_csv <- initial_data %>% 
  mutate(area = "WMT",
         home2 = "WMA") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_c != "Paused") %>% 
  # separate temp to remove instances of ">" in the temp data
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = datetime,
         date_sums = date,
         time_sums = time,
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         file_type = "logtag") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  filter(!is.na(temp_c_sums))

@@

# Format combined file from above
wmt_sums_csv_2 <- initial_data %>% 
  mutate(area = "WMT",
         home2 = "WMA",
         datetime_sums = ymd_hms(datetime_sums)) %>% 
  separate("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(date_sums = ymd(date_sums),
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         file_type = "temp_c") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  filter(!is.na(temp_c_sums))

@@

# Format combined file from above
wmt_sums_csv_3 <- initial_data %>% 
  mutate(area = "WMT",
         home2 = "WMA") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_f != "Paused") %>% 
  separate(temp_f, c("trash2", "temp_f"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = mdy_hms(datetime),
         date_sums = mdy(date),
         time_sums = time,
         temp_f = if_else(is.na(temp_f), trash2, temp_f),
         temp_f = as.numeric(temp_f),
         temp_c_sums = (temp_f-32)/1.8,
         file_type = "temp_f") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  filter(!is.na(temp_c_sums))

@@

# Format combined file from above
wmt_sums_xlsx <- initial_data %>% 
  mutate(datetime = ymd_hms(`Log data: date/time`),
         temp_c = as.numeric(`Temperature °C`),
         area = "WMT",
         home2 = "WMA") %>% 
  separate("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = datetime,
         date_sums = date,
         time_sums = time,
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         home = as.factor(home),
         file_type = "xlsx_c") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  filter(!is.na(temp_c_sums))

@@

# Format combined file from above
wmt_sums_xlsx2 <- initial_data %>% 
  mutate(datetime = ymd_hms(`Log data: date/time`),
         temp_c = as.numeric(`Temperature °C`),
         area = "WMT",
         home2 = "WMA") %>% 
  separate("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>%
  mutate(datetime_sums = datetime,
         date_sums = date,
         time_sums = time,
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         home = as.factor(home),
         file_type = "xlsx_c") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  filter(!is.na(temp_c_sums))

@@

# Format combined file from above
wmt_sums_xlsx3 <- initial_data %>% 
  mutate(datetime = ymd_hms(datetime),
         temp_c = as.numeric(temp_c),
         area = "WMT",
         home2 = "WMA") %>% 
  separate("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>%
  mutate(datetime_sums = datetime,
         date_sums = date,
         time_sums = time,
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         home = as.factor(home),
         file_type = "xlsx_c") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  filter(!is.na(temp_c_sums))

@@

# Format combined file from above
wmt_sums_xlsx4 <- initial_data %>% 
  mutate(temp_c = as.numeric(temp_c),
         area = "WMT",
         home2 = "WMA") %>% 
  separate("time", c("trash", "time"), sep = " ") %>%
  unite("time", c("time", "am_pm"), sep = " ") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>%
  mutate(datetime_sums = ymd_hms(datetime),
         date_sums = ymd(date),
         time_sums = time,
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         home = as.factor(home),
         file_type = "xlsx_c") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  filter(!is.na(temp_c_sums))

@@

# Format combined file from above
wmt_sums_xlsx5 <- initial_data %>% 
  mutate(temp_f = as.numeric(temp_f),
         area = "WMT",
         home2 = "WMA") %>% 
  separate("time", c("trash", "time"), sep = " ") %>%
  unite("time", c("time", "am_pm"), sep = " ") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  mutate(datetime_sums = ymd_hms(datetime),
         date_sums = ymd(date),
         time_sums = time,
         temp_c_sums = (temp_f-32)/1.8,
         home = as.factor(home),
         file_type = "xlsx_f") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  filter(!is.na(temp_c_sums))

# Bind all WMT SUMs data together
wmt_sums_raw <- rbind(wmt_sums_csv, wmt_sums_csv_2, wmt_sums_csv_3,
                      wmt_sums_xlsx, wmt_sums_xlsx2, wmt_sums_xlsx3,
                      wmt_sums_xlsx4, wmt_sums_xlsx5) %>% 
  select(-datetime_sums) %>% 
  unite("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  filter(!is.na(date_sums)) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% # remove duplicate lines that have same info from different files
  mutate(file_type = factor(file_type, levels = c("logtag", "temp_c",
                                                  "temp_f", "xlsx_c",
                                                  "xlsx_f")))

# This filtering will keep only the first instance when there are multiple
# observations for a specific datetime_sums
wmt_sums_filter <- wmt_sums_raw %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>% 
  ungroup() %>% 
  arrange(home, datetime_sums)

# write_rds(wmt_sums_filter, "Output/wmt_sums_raw.rds")
```

@@

# Format combined file from above
nn_sums_csv <- initial_data %>% 
  mutate(area = "NN") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = datetime,
         date_sums = date,
         time_sums = time,
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         file_type = "logtag") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  filter(!is.na(temp_c_sums))

@@

# Format combined file from above; combine with other PM data below
nn_sums_csv_2 <- initial_data %>% 
  mutate(area = "NN",
         datetime_sums = mdy_hm(datetime)) %>% 
  separate("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>%
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(date_sums = ymd(date_sums),
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         file_type = "temp_c") %>%
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  filter(!is.na(temp_c_sums))

# List files
## Numerous files had this format
## No header, 3 columns: date, time, temp (F)
list_csv_files_3 <- list.files("Input/NN/sums_csv_old/3col-f")

@@

# Bind all WMT SUMs data together
nn_sums_raw <- rbind(nn_sums_csv, nn_sums_csv_2, nn_sums_csv_3) %>% 
  select(-datetime_sums) %>% 
  unite("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  filter(!is.na(date_sums)) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  mutate(file_type = factor(file_type, levels = c("logtag", "temp_c",
                                                  "temp_f")))

# This filtering will keep only the first instance when there are multiple
# observations for a specific datetime_sums
nn_sums_filter <- nn_sums_raw %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>% 
  ungroup() %>% 
  arrange(home, datetime_sums)

# write_rds(nn_sums_filter, "Output/nn_sums_raw.rds")
```

@@

# Format combined file from above; combine with other PM data below
ak_sums_csv <- initial_data %>% 
  mutate(area = "AK") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>%
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = ymd_hms(datetime),
         date_sums = date,
         time_sums = time,
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         file_type = "logtag") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  filter(!is.na(temp_c_sums))

# List files
## Numerous files had this format with no header
## 5 columns: line, date, time, temp (F), notes
list_csv_files_2 <- list.files("Input/AK/sums_csv_old")

@@

# Format combined file from above; combine with other PM data below
ak_sums_xlsx <- initial_data %>% 
  mutate(area = "AK") %>% 
  separate("time", c("trash", "time"), sep = " ", remove = FALSE) %>% 
  unite("time", c("time", "am_pm"), sep = " ") %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(date_sums = ymd(date),
         time_sums = time,
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         home = as.factor(home),
         file_type = "xlsx_c") %>% 
  unite("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = ymd_hms(datetime_sums)) %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  filter(!is.na(temp_c_sums))

@@

# Format combined file from above; combine with other PM data below
ak_sums_xlsx2 <- initial_data %>% 
  mutate(area = "AK") %>% 
  separate("time", c("trash", "time"), sep = " ", remove = FALSE) %>% 
  unite("time", c("time", "am_pm"), sep = " ") %>% 
  mutate(date_sums = ymd(date),
         time_sums = time,
         temp_c_sums = as.numeric((temp_f-32)/1.8),
         home = as.factor(home),
         file_type = "xlsx_f") %>% 
  unite("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = ymd_hms(datetime_sums)) %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  filter(!is.na(temp_c_sums))

# Bind all AK SUMs data together
ak_sums_raw <- rbind(ak_sums_csv, ak_sums_csv_2, 
                     ak_sums_xlsx, ak_sums_xlsx2) %>% 
  select(-datetime_sums) %>% 
  unite("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  filter(!is.na(date_sums)) %>% 
  arrange(home, datetime_sums) %>% 
  distinct() %>% 
  mutate(file_type = factor(file_type, levels = c("logtag", "temp_f",
                                                  "xlsx_c", "xlsx_f")))

# This filtering will keep only the first instance when there are multiple
# observations for a specific datetime_sums
ak_sums_filter <- ak_sums_raw %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>% 
  ungroup() %>% 
  arrange(home, datetime_sums)

# write_rds(ak_sums_filter, "Output/ak_sums_raw.rds")
```

>>>>

---
title: "KidsAIR initial SUMs data work"
author: "Ethan Walker"
date: "Started 23 Dec 2019, Updated 30 Jan 2020"
output: pdf_document
---

@@

# Format combined file from above
wmt_sums_csv <- initial_data %>% 
  mutate(area = "WMT",
         home2 = "WMA") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_c != "Paused") %>% 
  # separate temp to remove instances of ">" in the temp data
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = ymd_hms(datetime),
         date_sums = ymd(date),
         time_sums = hms(time),
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         file_type = "logtag") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  filter(!is.na(temp_c_sums)) %>% 
  arrange(home, datetime_sums)

@@

# Format combined file from above
wmt_sums_csv_2 <- initial_data %>% 
  mutate(area = "WMT",
         home2 = "WMA",
         datetime_sums = ymd_hms(datetime_sums)) %>% 
  separate("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = ymd_hms(datetime_sums),
         date_sums = ymd(date_sums),
         time_sums = hms(time_sums),
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         file_type = "temp_c") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  filter(!is.na(temp_c_sums)) %>% 
  arrange(home, datetime_sums)

@@

# Format combined file from above
wmt_sums_csv_3 <- initial_data %>% 
  mutate(area = "WMT",
         home2 = "WMA") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_f != "Paused") %>% 
  separate(temp_f, c("trash2", "temp_f"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = mdy_hms(datetime),
         date_sums = mdy(date),
         time_sums = hms(time),
         temp_f = if_else(is.na(temp_f), trash2, temp_f),
         temp_f = as.numeric(temp_f),
         temp_c_sums = (temp_f-32)/1.8,
         file_type = "temp_f") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  mutate(datetime_sums = ymd_hms(datetime_sums),
         date_sums = ymd(date_sums)) %>% 
  arrange(home, datetime_sums) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  filter(!is.na(temp_c_sums)) %>% 
  arrange(home, datetime_sums)

@@

# Format combined file from above
wmt_sums_xlsx <- initial_data %>% 
  mutate(datetime = ymd_hms(`Log data: date/time`),
         temp_c = as.numeric(`Temperature °C`),
         area = "WMT",
         home2 = "WMA") %>% 
  separate("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = ymd_hms(datetime),
         date_sums = ymd(date),
         time_sums = hms(time),
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         home = as.factor(home),
         file_type = "xlsx_c") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  filter(!is.na(temp_c_sums)) %>% 
  arrange(home, datetime_sums)

@@

# Format combined file from above
wmt_sums_xlsx2 <- initial_data %>% 
  mutate(datetime = ymd_hms(`Log data: date/time`),
         temp_c = as.numeric(`Temperature °C`),
         area = "WMT",
         home2 = "WMA") %>% 
  separate("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>%
  mutate(datetime_sums = ymd_hms(datetime),
         date_sums = ymd(date),
         time_sums = hms(time),
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         home = as.factor(home),
         file_type = "xlsx_c") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  filter(!is.na(temp_c_sums)) %>% 
  arrange(home, datetime_sums)

@@

# Format combined file from above
wmt_sums_xlsx3 <- initial_data %>% 
  mutate(datetime = ymd_hms(datetime),
         temp_c = as.numeric(temp_c),
         area = "WMT",
         home2 = "WMA") %>% 
  separate("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>%
  mutate(datetime_sums = ymd_hms(datetime),
         date_sums = ymd(date),
         time_sums = hms(time),
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         home = as.factor(home),
         file_type = "xlsx_c") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  filter(!is.na(temp_c_sums)) %>% 
  arrange(home, datetime_sums)

@@

# Format combined file from above
wmt_sums_xlsx4 <- initial_data %>% 
  mutate(temp_c = as.numeric(temp_c),
         area = "WMT",
         home2 = "WMA") %>% 
  separate("time", c("trash", "time"), sep = " ") %>%
  unite("time", c("time", "am_pm"), sep = " ") %>%
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>%
  mutate(datetime_sums = ymd_hms(datetime),
         date_sums = ymd(date),
         time_sums = hms(time),
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         home = as.factor(home),
         file_type = "xlsx_c") %>% 
  select(home, area, datetime_sums, temp_c_sums, file_type) %>% 
  separate("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = ymd_hms(datetime_sums),
         date_sums = ymd(date_sums),
         time_sums = hms(time_sums)) %>% 
  arrange(home, datetime_sums) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  filter(!is.na(temp_c_sums)) %>% 
  arrange(home, datetime_sums)

@@

# Format combined file from above
wmt_sums_xlsx5 <- initial_data %>% 
  mutate(temp_f = as.numeric(temp_f),
         area = "WMT",
         home2 = "WMA") %>% 
  separate("time", c("trash", "time"), sep = " ") %>%
  unite("time", c("time", "am_pm"), sep = " ") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  unite("home", c("home2", "home"), sep = "") %>% 
  mutate(datetime_sums = ymd_hms(datetime),
         date_sums = ymd(date),
         time_sums = hms(time),
         temp_c_sums = (temp_f-32)/1.8,
         home = as.factor(home),
         file_type = "xlsx_f") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  separate("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = ymd_hms(datetime_sums),
         date_sums = ymd(date_sums),
         time_sums = hms(time_sums)) %>% 
  arrange(home, datetime_sums) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  arrange(home, datetime_sums)

# Bind all WMT SUMs data together
wmt_sums_raw <- rbind(wmt_sums_csv, wmt_sums_csv_2, wmt_sums_csv_3,
                      wmt_sums_xlsx, wmt_sums_xlsx2, wmt_sums_xlsx3,
                      wmt_sums_xlsx4, wmt_sums_xlsx5) %>% 
  filter(!is.na(datetime_sums)) %>% 
  mutate(file_type = factor(file_type, levels = c("logtag", "temp_c",
                                                  "temp_f", "xlsx_c",
                                                  "xlsx_f"))) %>% 
  arrange(home, datetime_sums, file_type) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  arrange(home, datetime_sums)

# write_rds(wmt_sums_raw, "Output/wmt_sums_raw.rds")
```

@@

# Format combined file from above
nn_sums_csv <- initial_data %>% 
  mutate(area = "NN") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = ymd_hms(datetime),
         date_sums = ymd(date),
         time_sums = hms(time),
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         file_type = "logtag") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  filter(!is.na(temp_c_sums)) %>% 
  arrange(home, datetime_sums)

@@

# Format combined file from above; combine with other PM data below
nn_sums_csv_2 <- initial_data %>% 
  mutate(area = "NN",
         datetime_sums = mdy_hm(datetime)) %>% 
  separate("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>%
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = ymd_hms(datetime_sums),
         date_sums = ymd(date_sums),
         time_sums = hms(time_sums),
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         file_type = "temp_c") %>%
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  filter(!is.na(temp_c_sums)) %>% 
  arrange(home, datetime_sums)

# List files
## Numerous files had this format
## No header, 3 columns: date, time, temp (F)
##### NO LONGER USING THESE FILES!
##### COMPARED TO CORRESPONDING LOGTAG FILES, THE TIMESTAMPS ARE OFF
list_csv_files_3 <- list.files("Input/NN/sums_csv_old/3col-f")

@@

# Bind all WMT SUMs data together
nn_sums_raw <- rbind(nn_sums_csv, nn_sums_csv_2) %>% 
  filter(!is.na(datetime_sums)) %>% 
  mutate(file_type = factor(file_type, levels = c("logtag", "temp_c"))) %>% 
  arrange(home, datetime_sums, file_type) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  arrange(home, datetime_sums)

# write_rds(nn_sums_raw, "Output/nn_sums_raw.rds")
```

@@

# Format combined file from above; combine with other PM data below
ak_sums_csv <- initial_data %>% 
  mutate(area = "AK") %>% 
  unite("datetime", c("date", "time"), sep = " ", remove = FALSE) %>%
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = ymd_hms(datetime),
         date_sums = ymd(date),
         time_sums = hms(time),
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         file_type = "logtag") %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  filter(!is.na(temp_c_sums)) %>% 
  arrange(home, datetime_sums)

# List files
## Numerous files had this format with no header
## 5 columns: line, date, time, temp (F), notes
##### NO LONGER USING THESE FILES!
##### COMPARED TO CORRESPONDING LOGTAG FILES, THE TIMESTAMPS ARE OFF
list_csv_files_2 <- list.files("Input/AK/sums_csv_old")

@@

# Format combined file from above; combine with other PM data below
ak_sums_xlsx <- initial_data %>% 
  mutate(area = "AK") %>% 
  separate("time", c("trash", "time"), sep = " ", remove = FALSE) %>% 
  unite("time", c("time", "am_pm"), sep = " ") %>% 
  filter(temp_c != "Paused") %>% 
  separate(temp_c, c("trash2", "temp_c"), sep = " ", remove = FALSE) %>% 
  mutate(date_sums = ymd(date),
         time_sums = time,
         temp_c = if_else(is.na(temp_c), trash2, temp_c),
         temp_c_sums = as.numeric(temp_c),
         home = as.factor(home),
         file_type = "xlsx_c") %>% 
  unite("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = ymd_hms(datetime_sums)) %>% 
  separate("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  mutate(date_sums = ymd(date_sums),
         time_sums = hms(time_sums)) %>% 
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  filter(!is.na(temp_c_sums)) %>% 
  arrange(home, datetime_sums)

@@

# Format combined file from above; combine with other PM data below
ak_sums_xlsx2 <- initial_data %>% 
  mutate(area = "AK") %>% 
  separate("time", c("trash", "time"), sep = " ", remove = FALSE) %>% 
  unite("time", c("time", "am_pm"), sep = " ") %>% 
  mutate(date_sums = ymd(date),
         time_sums = time,
         temp_c_sums = as.numeric((temp_f-32)/1.8),
         home = as.factor(home),
         file_type = "xlsx_f") %>% 
  unite("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_sums = ymd_hms(datetime_sums)) %>% 
  separate("datetime_sums", c("date_sums", "time_sums"), sep = " ", remove = FALSE) %>% 
  mutate(date_sums = ymd(date_sums),
         time_sums = hms(time_sums)) %>%
  select(home, area, datetime_sums, date_sums, time_sums, temp_c_sums, file_type) %>% 
  arrange(home, datetime_sums) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  filter(!is.na(temp_c_sums)) %>% 
  arrange(home, datetime_sums)

# Bind all AK SUMs data together
ak_sums_raw <- rbind(ak_sums_csv,  
                     ak_sums_xlsx, ak_sums_xlsx2) %>% 
  filter(!is.na(datetime_sums)) %>% 
  mutate(file_type = factor(file_type, levels = c("logtag",
                                                  "xlsx_c", "xlsx_f"))) %>% 
  arrange(home, datetime_sums, file_type) %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>%  # remove duplicate lines that have same info from different files
  ungroup() %>% 
  arrange(home, datetime_sums)

# write_rds(ak_sums_raw, "Output/ak_sums_raw.rds")
```
